---
title: "**AsYd - Asymmetry Detection**"
output:
  html_document:
    df_print: paged
runtime: shiny
---

```{r libraries, echo=FALSE, message=FALSE, warning=FALSE}

library(dplyr)
library(DT)
library(glue)
library(ggplot2)
library(gridExtra)
library(htmltools)
library(kableExtra)
library(knitr)
library(plotly)
library(rlang)
library(shiny)
library(shinythemes)
library(writexl)

```

<hr>

# Introduction

This R notebook is designed to examine and analyze asymmetries between two distinct data sources, namely MDE and National Data. The primary objective of this notebook is to conduct a thorough analysis employing a variety of tools, including descriptive analysis and selective editing techniques, with the intention of identifying and addressing the asymmetries observed between the two data sources.

```{r configs}

year  = "YYYY"
month = "MM"

input_path   = "your_data_input_path"
output_path  = "your_output_path"

filename_mde = "mde_data_filename.csv"
filename_nat = "national_data_filename.csv"

```

<hr>

# Data

Import the data. MDE and National data should be stored in separate .csv files. The columns should include a country code column, a product code column, an operator identifier column and a numeric value column.

```{r data import}

df_MDE <- read.csv(glue("{input_path}/{filename_mde}"))
df_NAT <- read.csv(glue("{input_path}/{filename_nat}"))

```

Map the variable names to your specific columns.

```{r variable mapping}

country_id  = "your_country_id"
product_id  = "your_product_id"
operator_id = "your_operator_id"
nat_value   = "your_nat_value"
mde_value   = "your_mde_value"

```

```{r mapped dfs, echo=FALSE}

df_MDE_map <- data.frame(country_id = df_MDE[[country_id]], 
                         product_id_8 = df_MDE[[product_id]], 
                         operator_id = df_MDE[[operator_id]], 
                         mde_value = df_MDE[[mde_value]])

df_NAT_map <- data.frame(country_id = df_NAT[[country_id]], 
                         product_id_8 = df_NAT[[product_id]], 
                         operator_id = df_NAT[[operator_id]], 
                         nat_value = df_NAT[[nat_value]])

```

## Data summary

Visualize the differences between two imported data sources, the distribution of inclusion status within the merged data frame and the count of distinct product classes.

<br>

```{r table mde vs nat, echo=FALSE}

# extract the variable counts from the MDE data source 
n_countries_MDE <- length(unique(df_MDE_map$country_id))
n_operators_MDE <- length(unique(df_MDE_map$operator_id))
n_products_MDE <- length(unique(df_MDE_map$product_id_8))
n_observations_MDE <- nrow(df_MDE_map)

# extract the variable counts from the National data source
n_countries_NAT <- length(unique(df_NAT_map$country_id))
n_operators_NAT <- length(unique(df_NAT_map$operator_id))
n_products_NAT <- length(unique(df_NAT_map$product_id_8))
n_observations_NAT <- nrow(df_NAT_map)

# convert the counts into a data frame
table_sources_raw <- data.frame(
  MDE = c(n_observations_MDE, n_countries_MDE, n_operators_MDE, n_products_MDE),
  National = c(n_observations_NAT, n_countries_NAT, 
               n_operators_NAT, n_products_NAT)
)

# define the raw names
row_names_sources <- c("n_observations", "n_countries", 
                       "n_operators", "n_products")
rownames(table_sources_raw) <- row_names_sources

# style the data frame as a table
table_sources <- kable(table_sources_raw, align = "r", 
                       caption = "MDE vs National Data") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE)

```

```{r merge data, echo=FALSE}

# merge MDE and National data into a single data frame
df <- merge(df_MDE_map, df_NAT_map, 
            by = c("country_id", "product_id_8", "operator_id"), all = TRUE)
df[c("nat_value", "mde_value")][is.na(df[c("nat_value", "mde_value")])] <- 0

# convert the columns to the appropriate types
df$country_id <- as.factor(df$country_id)
df$product_id_8 <- as.character(df$product_id_8)
df$operator_id <- as.character(df$operator_id)

# compute the inclusion status column
df$inclusion_status <- 
  ifelse(df$mde_value == 0 & df$nat_value != 0, 0,
  ifelse(df$mde_value != 0 & df$nat_value == 0, 1,
  ifelse(df$mde_value != 0 & df$nat_value != 0 & 
           df$mde_value != df$nat_value, 2,
  ifelse(df$mde_value == df$nat_value & df$mde_value != 0 & 
           df$nat_value != 0, 3, NA)))
)
df$inclusion_status <- as.factor(df$inclusion_status)

# extract additional product codes
df$product_id_2 <- substr(df$product_id_8, start = 1, stop = 2)
df$product_id_4 <- substr(df$product_id_8, start = 1, stop = 4)

# order the columns
columns <- c("country_id", "product_id_2", "product_id_4", "product_id_8", 
             "operator_id", "mde_value", "nat_value", "inclusion_status")
df <- df[, columns]

```

```{r inclusion status distribution, echo=FALSE}

# count the different inclusion status classes
n_status_0 <- sum(df$inclusion_status == 0)  
n_status_1 <- sum(df$inclusion_status == 1)  
n_status_2 <- sum(df$inclusion_status == 2)  
n_status_3 <- sum(df$inclusion_status == 3)  
n_total <- nrow(df)

# convert the counts into a data frame
table_inclusion_status_raw <- data.frame(
  n_observations = c(n_status_0, n_status_1, n_status_2, n_status_3, n_total)
)

# define the row names
row_names_inclusion_status <- c("MDE = 0, NAT ≠ 0", "MDE ≠ 0, NAT = 0", 
                                "MDE ≠ NAT, both ≠ 0", "MDE = NAT", "Total")
rownames(table_inclusion_status_raw) <- row_names_inclusion_status

# style the data frame as a table
table_inclusion_status <- kable(table_inclusion_status_raw, align = "r", 
                                caption = "Merged Data - Inclusion Status") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE)

```

```{r product id table, echo=FALSE}

# count the product ids
n_product_8 <- length(unique(df$product_id_8))
n_product_4 <- length(unique(df$product_id_4))
n_product_2 <- length(unique(df$product_id_2))

# convert the counts into a data frame
table_product_id_raw <- data.frame(
  n_classes = c(n_product_2, n_product_4, n_product_8)
)

# define the row names
row_names_product_id <- c("Product (2-digits)", "Product (4-digits)", 
                          "Product (8-digits)")
rownames(table_product_id_raw) <- row_names_product_id

# style the data frame as a table
table_product_id <- kable(table_product_id_raw, align = "r", 
                          caption = "Merged Data - Product IDs") %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE)

```


```{r display html summary tables, echo=FALSE}

# convert the tables to html 
table_sources_html <- as.character(table_sources)
table_inclusion_status_html <- as.character(table_inclusion_status)
table_product_id_html <- as.character(table_product_id)

# combine the html tables side by side
table_summary_html <- tagList(
  tags$div(style = "display: flex; justify-content: space-between;",
           HTML(table_sources_html),
           HTML(table_inclusion_status_html),
           HTML(table_product_id_html))
)

# display the combined table
table_summary_html

```

<hr>

# Exploratory Analysis

This interactive tool is aimed at the exploration and analysis of asymmetry patterns in the data. The app provides box plots, asymmetry distribution visuals, and operator-specific measures to gain valuable insights into the data. It is important to note that the box plot visualization makes use of the log values, therefore values equal to 0 are dropped.

<br>

```{r filter lists extraction, echo=FALSE}

# create lists of filters needed for the shiny apps 
country_list <- unique(as.character(df$country_id))
product_2_list <- unique(as.character(df$product_id_2))
product_4_list <- unique(as.character(df$product_id_4))
product_8_list <- unique(as.character(df$product_id_8))
operator_list <- unique(as.character(df$operator_id))

```

```{r operator by country count, echo=FALSE}

# build the data frame needed for the exploratory analysis tool 
operator_by_country <- aggregate(df$country_id, by = list(df$operator_id),
                                 FUN = function(x) length(unique(x)))

# redefine variable names
colnames(operator_by_country) <- c("operator_id", "country_count")
one_country <- sum(operator_by_country$country_count == 1)
multiple_countries <- sum(operator_by_country$country_count >= 2)

```

```{r exploratory analysis shiny app, echo=FALSE, warning=FALSE, shiny=TRUE}

ui <- fluidPage(
  
  navbarPage(
    
    "Exploratory Analysis",
    
      
## ------ UI - BOX PLOT VISUALIZATION ------------------------------------------
    tabPanel(      
      "Box-plots",
      sidebarLayout(
        sidebarPanel(
          selectInput("countryFilter", "Country", 
                      choices = c("All", country_list), selected = "All"),
          selectInput("product2Filter", "Product (2-digits)", 
                      choices = c("All", product_2_list), selected = "All"),
          selectInput("product4Filter", "Product (4-digits)", 
                      choices = c("All", product_4_list), selected = "All"),
          selectInput("product8Filter", "Product (8-digits)", 
                      choices = c("All", product_8_list), selected = "All"),
          selectInput("operatorFilter", "Operator", 
                      choices = c("All", operator_list), selected = "All"),
          actionButton("resetButton", "Reset Filters")
        ), 
        mainPanel(
          plotOutput("boxPlot")
        ) 
      )
    ), 

## ------ UI - ASYMMETRY DISTRIBUTION ------------------------------------------
    tabPanel(
      "Asymmetry Distribution",
      sidebarLayout(
        sidebarPanel(
          selectInput("countryFilter", "Country", 
                      choices = c("All", country_list), selected = "All"),
          selectInput("variableFilter", "Variable", 
                      choices = c("country_id", "product_id_2"))
        ), 
        mainPanel(
          plotlyOutput("distributionPlot")
        ) 
      ) 
    ), 

## ------ UI - OPERATOR INSIGHT ------------------------------------------------
    tabPanel(
      "Operator Insight",
      sidebarLayout(
        sidebarPanel(
          sliderInput("numOperators", "Operators to display", 
                      min = 1, max = 50, value = 20),
          selectInput("selectOperator", "Select operator", 
                      choices = operator_list),
          actionButton("filterButton", "Filter")
        ), 
        mainPanel(
          plotOutput("barPlot"),
          dataTableOutput("filteredData")
        ) 
      ) 
    ) 
  ) 
)

server <- function(input, output, session) {

##------ SERVER - BOXPLOT VISUALIZATION ----------------------------------------  
  
  # define a function to filter the data frame
  filtered_data <- reactive({
    df_filtered <- df
    
    if (input$countryFilter != "All") {
      df_filtered <- df_filtered %>% 
        filter(country_id == input$countryFilter)
    }
    if (input$product2Filter != "All") {
      df_filtered <- df_filtered %>% 
        filter(product_id_2 == input$product2Filter)
    }
    if (input$product4Filter != "All") {
      df_filtered <- df_filtered %>% 
        filter(product_id_4 == input$product4Filter)
    }
    if (input$product8Filter != "All") {
      df_filtered <- df_filtered %>% 
        filter(product_id_8 == input$product8Filter)
    }
    if (input$operatorFilter != "All") {
      df_filtered <- df_filtered %>% 
        filter(operator_id == input$operatorFilter)
    }
    
    return(df_filtered)
  })

  # define the logic of the reset button
  observeEvent(input$resetButton, {
    updateSelectInput(session, "countryFilter", selected = "All")
    updateSelectInput(session, "product2Filter", selected = "All")
    updateSelectInput(session, "product4Filter", selected = "All")
    updateSelectInput(session, "product8Filter", selected = "All")
    updateSelectInput(session, "operatorFilter", selected = "All")
  })

  # create the box plots 
  output$boxPlot <- renderPlot({
  
    ggplot(filtered_data(), aes(x = factor(1), 
                                y = log(mde_value), fill = "mde_value")) +
      geom_boxplot() +
      geom_boxplot(aes(x = factor(2), 
                       y = log(nat_value), fill = "nat_value")) +
      scale_fill_manual(values = c("mde_value" = "steelblue", 
                                   "nat_value" = "orange")) +
      labs(fill = "Variable", x = "", y = "Value") +
      facet_wrap(~factor(1)) +
      theme_bw() +
      theme(axis.text.x = element_blank(), 
            plot.title = element_text(size = 20, hjust = 0.5)) +
      ggtitle("MDE vs NAT values (log)")
  })

## ------ SERVER - ASYMMETRY DISTRIBUTION --------------------------------------
  
  # display the horizontal box plots of the distributions
  output$distributionPlot <- renderPlotly({
    if (input$countryFilter == "All") {
      filtered_df <- df
    }
    else {
    filtered_df <- df %>%
      filter(country_id == input$countryFilter)
    }
    
    plot_ly(filtered_df, x = ~(mde_value - nat_value), 
            y = ~get(input$variableFilter),
            type = "box", orientation = "h") %>%
    layout(yaxis = list(autorange = "reversed"))
  })
  
## ------ SERVER - OPERATOR INSIGHT --------------------------------------------

  # display the bar plot of the top operators by country count 
  output$barPlot <- renderPlot({
    numOperators <- input$numOperators
    
    top_operators <- operator_by_country %>%
      arrange(desc(country_count)) %>%
      head(numOperators)
    
    ggplot(top_operators, aes(x = reorder(operator_id, desc(country_count)), 
                              y = country_count, fill = operator_id)) +
      geom_bar(stat = "identity") +
      labs(x = "Operator ID", y = "Country Count") +
      ggtitle(paste("Top", numOperators, "Operators by Country Count")) +
      theme_minimal() +
      geom_text(aes(label = country_count), vjust = -0.5) +
      theme(legend.position = "none", 
            axis.text.x = element_text(angle = 90, hjust = 1))
  })
  
  # define a function to filter the data frame
  filtered_df <- reactive({
    req(input$filterButton)
    operator <- input$selectOperator
    filter(df, df$operator_id == operator)
    
  })
  
  # display the data frame filtered by operator
  output$filteredData <- renderDataTable({
    filtered_df()
  }, options = list(columnDefs = list(list(visible = FALSE, 
                                           targets = c("inclusion_status", 
                                                       "product_id_4",
                                                       "product_id_2",
                                                       "operator_id")))))
}

## ------ RUN THE SHINY APP ----------------------------------------------------
shinyApp(ui, server, options = list(height = 570))

```

<hr>

# Asymmetry Detection

## Systematic Errors

This section is designed to identify and analyze systematic errors by comparing national values and MDE values for specific operators. In particular, a systematic error is identified when the same value for MDE and national data sources is associated to a different product code.

<br>

```{r compute systematic errors, echo=FALSE}

# extract subsets from the merged data frame
df_nat_only <- df[df$inclusion_status == 0, c('product_id_8', 'country_id', 
                                              'operator_id', 'nat_value')]
df_mde_only <- df[df$inclusion_status == 1, c('product_id_8', 'country_id', 
                                              'operator_id', 'mde_value')]

# define the systematic error data frame
df_class_error <- merge(df_nat_only, df_mde_only,
                        by.x = c('operator_id', 'nat_value'),
                        by.y = c('operator_id', 'mde_value'),
                        suffix = c("_nat", "_mde"))
names(df_class_error)[names(df_class_error) == 'nat_value'] <- "value"

# order the data frame
df_class_error <- df_class_error[order(df_class_error$value, decreasing = TRUE), ]

```

```{r table of systematic errors, echo=FALSE}
datatable(df_class_error, extensions = 'Buttons', options = list(
  dom = 'Bfrtip',
  buttons = list('csv')
))
```

<hr>

## Selective Editing - Relative Contribution

This deterministic approach relies on manually analyzing the data and determining a threshold for cell-level asymmetry contribution based on different potential aggregations. The relative contribution to the total asymmetry is defined as follows: 

<br>

$$ C_i = \frac{(val_{MDE, i}-val_{NAT, i})}{\sum(|(val_{MDE, i}-val_{NAT, i})|)}*100$$
<br>

It is important to notice that the relative contribution is sensitive to the groupings applied to the data frame.

<br>

```{r relative contribution shiny app, echo=FALSE, warning=FALSE, shiny=TRUE}

ui <- fluidPage(
  navbarPage(
    "Relative Contribution",
    tabPanel(
      "Table",
      sidebarLayout(
        sidebarPanel(
          selectInput("groupbyCols", "Group by", 
                      choices = c('country_id', 'product_id_2', 'product_id_4', 
                                  'product_id_8', 'operator_id', 
                                  'inclusion_status'), 
                      selected = 'country_id', multiple = TRUE),
          numericInput("threshContr", "Threshold for |contr|:", 
                       min = 0, max = 100, value = 0.8, step = 0.1),
          br(),
          textOutput("meanOutput"),
          textOutput("medianOutput"),
          textOutput("sdOutput"),
          textOutput("cutOutObsOutput"),
          br(),
          actionButton("filterButton", "Filter")
        ),
        mainPanel(
          titlePanel("Relative Contribution Table"),
          DTOutput("table"),
          tags$hr(),
          conditionalPanel(
            condition = "input.filterButton",
            titlePanel("Filtered Data"),
            DTOutput("filteredData")
          )
        )
      )
    )
  )
)



server <- function(input, output, session) {

  filtered_data <- reactive({
    
    if (length(input$groupbyCols) > 0) {
      
      df_grouped <- df %>%
        group_by(across(all_of(input$groupbyCols), factor)) %>%
        summarise(
          mde_value = sum(mde_value),
          nat_value = sum(nat_value),
          diff = mde_value - nat_value
        ) %>%
        ungroup() %>%
        mutate(
          total_diff_sum = sum(abs(diff))
        )
      
      df_filtered <- df_grouped %>%
        mutate(
          contr = round((diff/total_diff_sum)*100, digits = 3)
        ) %>%
        filter(abs(contr) >= input$threshContr)
      
    } else {
      
      df_filtered <- df %>%
        mutate(
          diff = mde_value - nat_value,
          contr = round((diff / sum(abs(diff))) * 100, digits = 3)
        ) %>%
        filter(abs(contr) >= input$threshContr)
    }
    
    return(df_filtered)
    
  })
  
  output$table <- renderDT({
    datatable(filtered_data(), class = 'cell-border stripe', 
              rownames = FALSE, filter = 'top', 
              editable = TRUE, extensions = c('Buttons'), options = list(
                dom = 'Bfrtip',
                buttons = list('colvis', 'csv'),
                width = '100%',
                scrollX = TRUE,
                columnDefs = list(list(targets = 'total_diff_sum', 
                                       visible = FALSE))
              ), selection = list(mode = 'single', target = 'row'))
  })
  
  output$meanOutput <- renderText({
    filtered_df <- filtered_data()
    mean_value <- mean(abs(filtered_df$contr))
    paste("Mean: ", round(mean_value, digits = 2))
  })
  
  output$medianOutput <- renderText({
    filtered_df <- filtered_data()
    median_value <- median(abs(filtered_df$contr))
    paste("Median: ", round(median_value, digits = 2))
  })
  
  output$sdOutput <- renderText({
    filtered_df <- filtered_data()
    sd_value <- sd(abs(filtered_df$contr))
    paste("SDev: ", round(sd_value, digits = 2))
  })

  filtered_total_data <- reactive({
    req(input$filterButton)
    
    filtered_df <- filtered_data()
    raw_df <- df
  
    # Check if column exists before extracting the list
    country_list_temp <- if ("country_id" %in% colnames(filtered_df))
      unique(as.character(filtered_df$country_id))
    else NULL
  
    product_2_list_temp <- if ("product_id_2" %in% colnames(filtered_df))
      unique(as.character(filtered_df$product_id_2))
    else NULL
  
    product_4_list_temp <- if ("product_id_4" %in% colnames(filtered_df))
      unique(as.character(filtered_df$product_id_4))
    else NULL
  
    product_8_list_temp <- if ("product_id_8" %in% colnames(filtered_df))
      unique(as.character(filtered_df$product_id_8))
    else NULL
  
    operator_list_temp <- if ("operator_id" %in% colnames(filtered_df))
      unique(as.character(filtered_df$operator_id))
    else NULL
  
    # Filter raw_df based on the extracted lists
    if (!is.null(country_list_temp)) {
      raw_df <- raw_df[raw_df$country_id %in% country_list_temp, ]
    }
    
    if (!is.null(product_2_list_temp)) {
      raw_df <- raw_df[raw_df$product_id_2 %in% product_2_list_temp, ]
    }
  
    if (!is.null(product_4_list_temp)) {
      raw_df <- raw_df[raw_df$product_id_4 %in% product_4_list_temp, ]
    }
  
    if (!is.null(product_8_list_temp)) {
      raw_df <- raw_df[raw_df$product_id_8 %in% product_8_list_temp, ]
    }
  
    if (!is.null(operator_list_temp)) {
      raw_df <- raw_df[raw_df$operator_id %in% operator_list_temp, ]
    }
  
    # Return the filtered raw_df
    raw_df
  })

  
  # display the filtered data frame
  output$filteredData <- renderDT({
    datatable(filtered_total_data(), class = 'cell-border stripe', rownames = FALSE, filter = 'top', 
              editable = TRUE, extensions = c('Buttons'), options = list(
                dom = 'Bfrtip',
                buttons = list('colvis', 'csv'),
                width = '100%',
                scrollX = TRUE,
                columnDefs = list(list(targets = c('product_id_2', 'product_id_4'), visible = FALSE))
              ), selection = list(mode = 'single', target = 'row'))
  })
  
}

shinyApp(ui, server, options = list(height = 730))

```

<hr>

## Selective Editing - Suspicion Index

The selective editing approach relies on two primary indexes for determining which values to edit. The first index is a distributional index. The second index is a suspicion index calculated using the inter-quantile range. By considering both of these indexes in combination, the selective editing approach determines which values should be targeted for editing. The suspicion index is defined as follows:

<br>

$$
S_i = \left\{
\begin{array}{ll}
    \frac{Q_1 - \log R_i}{Q_3 - Q_1}, \ \text{if} \ \log R_i < Q_1 \\
    \frac{\log R_i - Q_3}{Q_3 - Q_1}, \ \text{if} \ \log R_i > Q_3 \\
    0, \ \text{otherwise} \\
\end{array} \right.
$$
<br>

where $Q_1$ and $Q_3$ are the $25^{th}$ and $75^{th}$ percentiles of the distribution of the difference between MDE and National values in log scale. 

The distributional index is defined as follows:

<br>

$$
D_i = \left( 1-\frac{\max(S_{i})}{\sum S_i} \right)*100
$$
<br>

where $S_i$ represent the suspicion index of the $i^{th}$ operator.

<br>

```{r log-ratio computation, echo=FALSE}
df_filter <- subset(df, inclusion_status == 2)

df_filter$value_ratio <- df_filter$mde_value/df_filter$nat_value
df_filter$log_ratio <- log(df_filter$value_ratio)
```

```{r suspicion index shiny app, echo=FALSE, warning=FALSE, shiny=TRUE}

ui <- fluidPage(
  
  navbarPage(
    
    "Suspicion Index",

## ------ UI - TABLE -----------------------------------------------------------
    tabPanel(
      "Table",
      sidebarLayout(
        sidebarPanel(
          selectInput("countryFilter", "Country", choices = country_list, selected = "FR"),
          selectInput("productFilter", "Product (4-Digits)", choices = product_4_list, selected = "1022"),
          sliderInput("suspicionThreshold", "Threshold Suspicion Index", min = 0, max = 20, value = 8.0),
          sliderInput("distributionThreshold", "Threshold Distribution Index", min = 0, max = 100, value = 0.0),
          br(),
          textOutput("percObs"),
          textOutput("absObs"),
          br(),
          actionButton("filterButton", "Filter")
        ),
        mainPanel(
          titlePanel("Suspicion Index Table"),
          DTOutput("suspicionTable"),
          tags$hr(),
          conditionalPanel(
            condition = "input.filterButton",
            titlePanel("Filtered Data"),
            DTOutput("filteredData")
          )
        )
      )
    )
  )
)


server <- function(input, output, session) {
  
  # define a function to filter the data
  filtered_data <- reactive({
    data <- df_filter
    
    data <- data %>% 
        filter(country_id == input$countryFilter) %>%
        filter(product_id_4 == input$productFilter)
    
    return(data)
  })
  
  # define a function to compute the indexes
  suspicion_data <- reactive({
    
    data <- filtered_data()
    
    q1_q3 = quantile(data$log_ratio, probs = c(0.25, 0.75), na.rm = TRUE)
    log_ratio_Q1 <- q1_q3["25%"]
    log_ratio_Q3 <- q1_q3["75%"]
    interquantile_range <- log_ratio_Q3 - log_ratio_Q1
    
    data$suspicion_index_i <- (data$log_ratio < log_ratio_Q1) * (log_ratio_Q1 - data$log_ratio) / interquantile_range +
    (data$log_ratio > log_ratio_Q3) * (data$log_ratio - log_ratio_Q3) / interquantile_range

    return(data)
  })
  
  # define a function to aggregate data by operator
  aggregated_data <- reactive({
  
    aggregated_df <- suspicion_data() %>%
      group_by(operator_id) %>%
      summarize(
        suspicion_index = sum(suspicion_index_i),
        count_suspicion = length(suspicion_index_i),
        npos_suspicion = sum(suspicion_index_i > 0),
        distribution_index = as.numeric((1 - (max(suspicion_index_i) / suspicion_index))*100),
        sum_mde_value = sum(mde_value),
        sum_nat_value = sum(nat_value),
        sum_log_ratio = sum(log_ratio)
      )
    min_nonzero <- min(aggregated_df$distribution_index[aggregated_df$distribution_index != 0], na.rm = TRUE)
    
    aggregated_df$distribution_index[aggregated_df$distribution_index == 0 | is.nan(aggregated_df$distribution_index)] <- min_nonzero

    return(aggregated_df)
  })
  
  # define a function to filter the aggregated df
  filtered_aggregated_data <- reactive({
    
    data <- aggregated_data() %>%
      filter(suspicion_index >= input$suspicionThreshold) %>%
      filter(distribution_index >= input$distributionThreshold)
    
    return(data)
  })
  
  output$suspicionTable <- renderDataTable({
    
    datatable(filtered_aggregated_data(), class = 'cell-border stripe', rownames = FALSE, filter = 'top',
          editable = TRUE, extensions = c('Buttons'),
          options = list(
            dom = 'Bfrtip',
            buttons = list('colvis', 'csv'),
            width = '100%',
            scrollX = TRUE,
            columnDefs = list(list(targets = c('count_suspicion', 'npos_suspicion', 'sum_mde_value', 'sum_nat_value', 'sum_log_ratio'), visible = FALSE))
          ), selection = list(mode = 'single', target = 'row')) %>%
      formatRound(columns=c('suspicion_index', 'distribution_index'), digits=2)
  })
  
  # define a function to filter the total data frame
  filtered_total_data <- reactive({
    
    req(input$filterButton)
    
    filtered_df <- filtered_aggregated_data()
    raw_df <- df
  
    operator_list <- unique(as.character(filtered_df$operator_id))
    
    filtered_total_df <- raw_df %>%
      filter(country_id == input$countryFilter) %>%
      filter(product_id_4 == input$productFilter) %>%
      filter(operator_id %in% operator_list)
  
    # Return the filtered data frame
    return(filtered_total_df)
  })
  
  # display the filtered data frame
  output$filteredData <- renderDT({
    datatable(filtered_total_data(), class = 'cell-border stripe', rownames = FALSE, filter = 'top', 
              editable = TRUE, extensions = c('Buttons'), options = list(
                dom = 'Bfrtip',
                buttons = list('colvis', 'csv'),
                width = '100%',
                scrollX = TRUE,
                columnDefs = list(list(targets = c('product_id_2', 'product_id_4'), visible = FALSE))
              ), selection = list(mode = 'single', target = 'row'))
  })
  
  output$percObs <- renderText({
    filtered_df <- filtered_total_data()
    total_df <- filtered_data()
    len_filtered_df <- nrow(filtered_df)
    len_total_df <- nrow(total_df)
    perc_obs <- (len_filtered_df*100)/len_total_df
    paste("Filtered observations: ", round(perc_obs, digits = 2), "%")
  })
  
  output$absObs <- renderText({
    filtered_df <- filtered_total_data()
    total_df <- filtered_data()
    len_filtered_df <- nrow(filtered_df)
    len_total_df <- nrow(total_df)
    paste(len_filtered_df, " out of ", len_total_df, " observations")
  })
  
  # define a function to export the full data frame and the log file
  output$exportButton <- downloadHandler(
    # logic under development
  )
  
}

shinyApp(ui, server, options = list(height = 650))

```

<hr>